\Huge{\textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}

### 2021-04-05 paper/paper.tex
stuff, didn't clean up

\documentclass[a4paper, 12pt]{report}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage[strings]{underscore}
\usepackage{dirtytalk}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[acronym,toc]{glossaries}

@@

\begin{center}
	\begin{figure}[!htb]
		\includegraphics[width=\textwidth,keepaspectratio]{NoferBlock}
		\caption{An example of a \gls{blockchain} \cite{blockchain}} 
		\label{fig:middleware}
	\end{figure}
\end{center}

@@

@@

>>>>

\documentclass[a4paper, 12pt]{report}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage[strings]{underscore}
\usepackage{dirtytalk}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{float}
\usepackage{hyperref}
\usepackage[acronym,toc]{glossaries}

@@

\begin{center}
	\begin{figure}[H]
		\includegraphics[width=\textwidth,keepaspectratio]{NoferBlock}
		\caption{An example of a \gls{blockchain} \cite{blockchain}} 
		\label{fig:middleware}
	\end{figure}
\end{center}

@@

\section{Distributed Systems}
The primary reference used for distributed systems was Tanenbaum and van Steen's \say{Distributed Systems: Principles and Paradigms}\cite{tanenbaumdist}, who's literature provides an in-depth explanation from the fundamental theory of distributed systems to the design and implementation of such systems. Key details that were taken from this publication are detailed below. In general, this book covered the essential components of creating a distributed system, however much of the detail with regards to client-server interactions was not applicable to this project due to it's decentralised nature. Furthermore, a large portion of the book was not of interest to this project as it focuses on distributed processing, which only comprises a small element of this project, hence a large volume of information regarding implementation of processing was not useful.

\subsection{Architecture}
Tanenbaum and van Steen cover many aspects of a distributed system's architecture spanning network, software and physical architecture. This project will implement a decentralised, peer-to-peer network architecture, which will be discussed in detail in section \ref{decentrailsed}. The software used will consist primary of \gls{stub}s, which are used to hide the differences in machine architecture and communication between the computer and the distributed system. The combined use of \gls{stub}s creates a new software layer, known as \gls{middleware} which provides a common interface between a client application, and the distributed system. Creating this layer enables applications to communicate via an application-level protocol, which is independent from the protocol spoken by the \gls{middleware}.

\begin{figure}[H]
\centering
\includegraphics[height=5cm,keepaspectratio]{appl_layer_proto}
\caption{Application layer protocol running over \gls{middleware} \cite{tanenbaumdist}} 
\label{fig:middleware}
\end{figure}

With regards to physical architecture, Tanenbaum and van Steen discuss a number of approaches to client-server architectures, however due to the decentralised nature of this project, non of Tanenbaum and van Steen's classifications apply.

\subsection{Remote Procedure Calls (RPC)}
Tanenbaum and van Steen introduce the concept of a \acrfull{RPC}. \acrshort{RPC}s are used to execute some action on a remote node within a distributed system.  Tanenbaum and van Steen provide a concise breakdown of the steps required to execute an \acrshort{RPC}:

\begin{enumerate}
    \item The client procedure calls the client \gls{stub} in the normal way.
    \item The client \gls{stub} builds a message and calls the local \acrfull{OS}.
    \item The client \acrshort{OS} sends the message to the remote \acrshort{OS}.
    \item The remote \acrshort{OS} gives the message to the server \gls{stub}.
    \item The server \gls{stub} unpacks the parameters and calls the server.
    \item The server does the work and returns the result to the \gls{stub}.
    \item The server \gls{stub} packs it in a message and calls it's local \acrshort{OS}.
    \item The server's \acrshort{OS} send the message to the client's acrshort{OS}.
    \item The client's \acrshort{OS} sends the message to the client \gls{stub}.
    \item The \gls{stub} unpacks the result and returns to the client.
\end{enumerate}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth,keepaspectratio]{rpc}
\caption{A breakdown of an \acrshort{RPC} \cite{tanenbaumdist}} 
\label{fig:rpc}
\end{figure}

\section{Decentralised Systems} \label{decentrailsed}

\section{Blockchain}
The primary reference used for blockchain was Nofer et al.'s \say{Blockchain}\cite{blockchain}.

\section{Distributed Security}

\section{Firewall Rules}

\section{Fault Tolerance}

\section{Inter-Process Communication (IPC)}

@@

\appendix

%\iffalse
\chapter{Framework Source Code}
\lstinputlisting[language=c,style=c,caption=main.c,basicstyle=\ttfamily\scriptsize]{../src/main.c}
\lstinputlisting[language=c,style=c,caption=blockchain.h,basicstyle=\ttfamily\scriptsize]{../src/blockchain.h}
\lstinputlisting[language=c,style=c,caption=blockchain.c,basicstyle=\ttfamily\scriptsize]{../src/blockchain.c}
\lstinputlisting[language=c,style=c,caption=firewall.h,basicstyle=\ttfamily\scriptsize]{../src/firewall.h}
\lstinputlisting[language=c,style=c,caption=firewall.c,basicstyle=\ttfamily\scriptsize]{../src/firewall.c}
\lstinputlisting[language=c,style=c,caption=ipc.h,basicstyle=\ttfamily\scriptsize]{../src/ipc.h}
\lstinputlisting[language=c,style=c,caption=ipc.c,basicstyle=\ttfamily\scriptsize]{../src/ipc.c}
\lstinputlisting[language=c,style=c,caption=net.h,basicstyle=\ttfamily\scriptsize]{../src/net.h}
\lstinputlisting[language=c,style=c,caption=net.c,basicstyle=\ttfamily\scriptsize]{../src/net.c}
\lstinputlisting[language=c,style=c,caption=socket.h,basicstyle=\ttfamily\scriptsize]{../src/socket.h}
\lstinputlisting[language=c,style=c,caption=socket.c,basicstyle=\ttfamily\scriptsize]{../src/socket.c}

\chapter{Client Program Source Code}
\lstinputlisting[language=c,style=c,caption=client.c,basicstyle=\ttfamily\scriptsize]{"../src/example\string_client/client.c"}

\chapter{Code and Framework Documentation}
\includepdf[pages=-]{../docs/latex/refman.pdf}
%\fi
